Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Added a "general table"

>>>>

\begin{table}[H]
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 3.848      \\ \hline
Amount of lines                                                                                         & 8.284.140  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
Amount of tokens                                                                                        & 66.964.270 \\ \hline
Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
Amount of clone classes                                                                                 & 34.367     \\ \hline
\end{tabular}
\end{table}
